Bricking up and overgrowing backdoors in Intrusion Detection Systems

### 2019-09-06 ex2/paper/paper.tex
Add pruning figure

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%%
%% IMPORTANT NOTICE:
%%
%% For the copyright see the source file.
%%
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%%
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%%
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[10pt,sigconf,letterpaper]{acmart}
\acmYear{2019}
\copyrightyear{2019}
\acmConference{CoNEXT '19}{December 9-12, 2019}{Orlando, Florida, USA}

\usepackage{multirow}
\usepackage{blindtext}

@@

\newacronym{dl}{DL}{Deep Learning}
\newacronym{ml}{ML}{Machine Learning}
\newacronym{ale}{ALE}{Accumulated Local Effects}
\newacronym{mui}{MuI}{Model Under Investigation}
\newacronym{ttl}{TTL}{Time-to-Live}
\newacronym{pdp}{PDP}{Partial Dependence Plot}
\newacronym{ale}{ALE}{Accumulated Local Effects}
\newacronym{ids}{IDS}{Intrusion Detection System}

@@

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Maximilian Bachl}
\affiliation{\institution{Technische Universit\"at Wien}}
%\authornote{Both authors contributed equally to this research.}
\email{maximilian.bachl@tuwien.ac.at}

\author{Alexander Hartl}
\affiliation{\institution{Technische Universit\"at Wien}}
%\authornotemark[1]
\email{alexander.hartl@tuwien.ac.at}

\author{Tanja Zseby}
\affiliation{\institution{Technische Universit\"at Wien}}
\email{tanja.zseby@tuwien.ac.at}

\author{Joachim Fabini}
\affiliation{\institution{Technische Universit\"at Wien}}
\email{joachim.fabini@tuwien.ac.at}

@@

\subsubsection{Spotting Backdoors}
Backdoors can be identified by computing PDP and or ALE plots for the \gls{mui} and investigating if regions exist which have counter-intuitive model predictions.
\subsection{Pruning Techniques}
\subsubsection{Neural Network Pruning}
\subsubsection{Random Forest Pruning}
\subsection{Neural Network Fine-Tuning}

>>>>

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%%
%% IMPORTANT NOTICE:
%%
%% For the copyright see the source file.
%%
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%%
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%%
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[10pt,sigconf,letterpaper,dvipsnames]{acmart}
\acmYear{2019}
\copyrightyear{2019}
\acmConference{CoNEXT '19}{December 9-12, 2019}{Orlando, Florida, USA}

\usepackage[utf8]{inputenc}

\usepackage{multirow}
\usepackage{blindtext}
\usepackage{soul}

@@

\newacronym{dl}{DL}{Deep Learning}
\newacronym{ml}{ML}{Machine Learning}
\newacronym{cnn}{CNN}{Convolutional Neural Network}
\newacronym{ale}{ALE}{Accumulated Local Effects}
\newacronym{mui}{MuI}{Model Under Investigation}
\newacronym{ttl}{TTL}{Time-to-Live}
\newacronym{pdp}{PDP}{Partial Dependence Plot}
\newacronym{ale}{ALE}{Accumulated Local Effects}
\newacronym{ids}{IDS}{Intrusion Detection System}
\newacronym{nids}{NIDS}{Network Intrusion Detection System}

@@

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{Maximilian Bachl}
\affiliation{\institution{Technische Universität Wien}}
%\authornote{Both authors contributed equally to this research.}
\email{maximilian.bachl@tuwien.ac.at}

\author{Alexander Hartl}
\affiliation{\institution{Technische Universität Wien}}
%\authornotemark[1]
\email{alexander.hartl@tuwien.ac.at}

\author{Joachim Fabini}
\affiliation{\institution{Technische Universität Wien}}
\email{joachim.fabini@tuwien.ac.at}

\author{Tanja Zseby}
\affiliation{\institution{Technische Universität Wien}}
\email{tanja.zseby@tuwien.ac.at}

@@

\subsubsection{Spotting Backdoors}
Backdoors can be identified by computing PDP and or ALE plots for the \gls{mui} and investigating if regions exist which have counter-intuitive model predictions.
\subsection{Pruning Techniques}
\subsubsection{Neural Network Pruning}
\subsubsection{Random Forest Pruning}
For intrusion detection decision tree based models or random forests of decision trees have been shown to usually achieve higher accuracy than multilayer perceptrons \todo{citation needed} and moreover they are generally faster to train and possibly more interpretable. For \glspl{nids} we thus consider the removal of backdoors from decision tree based models to be a more pressing issue than from multilayer perceptrons.

The defense mechanism proposed by \cite{biggio_bagging_2011} uses bagging to try to minimize the influence of a backdoor that is introduced in the training dataset via poisoning and is applicable to decision trees. However, this approach cannot protect if a trained model is obtained from another (untrusted) party in which the other party might potentially have introduced a backdoor.

We thus envision a defense approach that can be used for similar use cases like the mechanisms recently proposed for \glspl{cnn}.

\begin{figure*}[h]
\includegraphics[width=\textwidth]{pruning_example.pdf}

\caption{Example of a decision tree being pruned. Next to each leaf we show \textcolor{MidnightBlue}{the number of times a leaf was used} by validation samples and its \textcolor{Fuchsia}{depth} in the decision tree. We also highlight leaves, which indicate that a sample is \protect\sethlcolor{green} \hl{harmless} because these are the ones our algorithm considers as candidates for pruning. The leaf that is going to be cut in each step has a dashed connection to its parent. This decision tree is not functional anymore in the end because all its leaves indicate that a sample is an attack. However, the decision trees that we prune usually have several thousands of leaves and we never prune until the very end and thus this case of a degenerate decision tree is not problematic.}
\label{fig:pruningExample}
\end{figure*}

\subsection{Neural Network Fine-Tuning}
